### 2022-08-12 paper/Chapters/Chapter05.tex
update paper

\section{Trining on Higher Resolution}
We also trained our models on a higher resolution dataset with $ 512 \times 512 $ in width and height for each scene. Higher resolution data provides more information about surface features using the same model compared to lower resolutions. The advantage is that if we extract a fixed size patch from the normal map, say $32\times32$, it may correspond to a hind leg of the dragon object at a resolution of $128 \times 128$ scene, but at a resolution of $512\times 512$ scene, it may only correspond to a toe. Thus, if we still use the same kernel size in the network for the same data set (as in $ 3\times 3 $), the higher the resolution, the smaller the corresponding surface area. 
Thus, for the higher resolution, the surface becomes smoother and the surface normal can be computed more easily in a fixed size of area compare to lower resolution. This is a good thing. Because then we may only need to use these $ 32\ times 32 $ points to calculate a toe in an image with $ 512\ times512 $ resolution. But in an image with a resolution of $ 128\times128 $, the same area $ 32\times32 $ could correspond to the entire hind leg of the dragon object. In other words. Thus, the higher resolution helps the model to compute a more accurate normal map.

>>>>

\section{Trining on Higher Resolution}
We also trained our models on a higher resolution dataset with $ 512 \times 512 $ in width and height for each scene. Higher resolution data provides more information about surface features using the same model compared to lower resolutions. The advantage is that if we extract a fixed size patch from the normal map, say $32\times32$, it may correspond to a hind leg of the dragon object at a resolution of $128 \times 128$ scene, but at a resolution of $512\times 512$ scene, it may only correspond to a toe. Thus, if we still use the same kernel size in the network for the same data set ($ 3\times 3 $), the higher the resolution, the smaller the corresponding surface area. 
Thus, for the higher resolution, the surface becomes smoother and the surface normal can be computed more easily in a fixed size of area compare to lower resolution. This is a good thing. Because then we may only need to use these $ 32\times 32 $ points to calculate a toe in an image with $ 512\times512 $ resolution. But in an image with a resolution of $ 128\times128 $, the same area $ 32\times32 $ could correspond to the entire hind leg of the dragon object. In other words. Thus, the higher resolution helps the model to compute a more accurate normal map.

### 2022-08-12 paper/Chapters/Chapter06.tex
update paper

The second network is called Trip-Net and is based on the GCNN model. It is designed for illumination-calibrated RGB-D image-based approaches. This model uses the GCNN architecture three times to process vertex map, light map and image separately. We have also found that 4 fusions of the 3 pipes in our models is the key to performance improvement.
Our experiments show that the models trained on illuminated calibrated RGB-D images perform better than an approach based only on geometry information and provide more sharpness in the normal map.

>>>>

The second network is called Trip-Net and is based on the GCNN model. It is designed for illumination-calibrated RGB-D image-based approaches. This model uses the GCNN architecture three times to process vertex map, light map and image separately. We also found that 4 fusions of the 3 pipes in our models is the key point to improve the performance.
Based on our proposed dataset with resolution $ 128\times 128 $, the experiments show that the models trained on illuminated calibrated RGB-D images improve the accuracy by $ 11.1\% $ of the average degree error compared to the geometry information based approach, which provides more sharpness in the normal map.
